Improved Global Routing By Using A Star Algorithm

### 2020-06-01 paper.tex
Third Related Work Paper

In \cite{b1} a sequential global routing is used and two bounded length maze algorithms as finding path algorithms are provided in order to make the router faster and to avoid congestions thus avoiding overflow, the first one is optimal-BLMR and the second one is heuristic-BLMR. optimal-BLMR is used to get the minimum cost paths to be used as routing paths, this can be done in three steps. First BLC (bounded length constraint) is defined as a greater number than Manhattan distance then to go from source to target the neighbor points are tested if it can be a part of a path or not, each point that violates the BLC constraint is discarded. Second, if the route Started from point \textit{v}, ended at point \textit{u} and there were many paths between these two points, the normal maze algorithm will take the path with the minimum cost which may cause the route to pass through congestions, but in optimal-BLMR, it keeps track of all paths between these two points in order to choose the path that will not cause overflow, it iterates on the minimum cost path every time and if it found a suitable path it reserves that path, otherwise, it discards that path. Third step the optimal-BLMR iterates on the reserved paths and choose the one to be used for routing. Heuristic-BLMR is used to speed the router up by reserving only one path between the two points, but it has to keep the advantage of optimal-BLMR (avoiding congestions), this can be achieved by reserving the selected path only if the wire length is enough to detour around congested regions. The advantages of this paper are using sequential global routing which is based on multithreaded global routing which speedup the router between $2.71$ and $3.12$ in overflow free cases, avoiding collision by using optimal-BLMR, and making a fast and nearly avoiding collision algorithm (heuristic-BLMR). But there are some disadvantages too, as optimal-BLMR is very slow to be used, although heuristic-BLMR is faster than optimal-BLMR its results are not accurate as the wire length is not the best compared with other papers, and it is done on \textit{2D} grid then it is projected to the \textit{3D} one however, this approach gives a good result but it is not accurate like routers that apply routing in the \textit{3D} grid directly as in \cite{b9}.

@@

@@

    \bibitem{b14} Xu, Yue, and Chris Chu. "MGR: Multi-level global router." \textit{2011 IEEE/ACM International Conference on Computer-Aided Design (ICCAD)}. IEEE, 2011.

>>>>

In \cite{b1}, a sequential global routing is used and two bounded length maze algorithms as finding path algorithms are provided in order to make the router faster and to avoid congestions thus avoiding overflow, the first one is optimal-BLMR and the second one is heuristic-BLMR. optimal-BLMR is used to get the minimum cost paths to be used as routing paths, this can be done in three steps. First BLC (bounded length constraint) is defined as a greater number than Manhattan distance then to go from source to target the neighbor points are tested if it can be a part of a path or not, each point that violates the BLC constraint is discarded. Second, if the route Started from point \textit{v}, ended at point \textit{u} and there were many paths between these two points, the normal maze algorithm will take the path with the minimum cost which may cause the route to pass through congestions, but in optimal-BLMR, it keeps track of all paths between these two points in order to choose the path that will not cause overflow, it iterates on the minimum cost path every time and if it found a suitable path it reserves that path, otherwise, it discards that path. Third step the optimal-BLMR iterates on the reserved paths and choose the one to be used for routing. Heuristic-BLMR is used to speed the router up by reserving only one path between the two points, but it has to keep the advantage of optimal-BLMR (avoiding congestions), this can be achieved by reserving the selected path only if the wire length is enough to detour around congested regions. The advantages of this paper are using sequential global routing which is based on multithreaded global routing which speedup the router between $2.71$ and $3.12$ in overflow free cases, avoiding collision by using optimal-BLMR, and making a fast and nearly avoiding collision algorithm (heuristic-BLMR). But there are some disadvantages too, as optimal-BLMR is very slow to be used, although heuristic-BLMR is faster than optimal-BLMR its results are not accurate as the wire length is not the best compared with other papers, and it is done on \textit{2D} grid then it is projected to the \textit{3D} one however, this approach gives a good result but it is not accurate like routers that apply routing in the \textit{3D} grid directly as in \cite{b9}.

@@

In \cite{b15}, routing efficiency is increased compared to \textit{2D} routers, and runtime is decreased compared to \textit{3D} routers. As the \textit{3D} routers achieve efficient results, it will be used but with some modifications to achieve an acceptable runtime. At first, initialization is done by running a Steiner tree, pattern routing step, and dynamic programming is used in layer assignment as in \textit{2D} routers like \cite{b4}. The second step named coarsening stage, in which, the \textit{3D} grid is split into a hierarchy of levels, a \textit{3D} maze routing is done on each level, starting with the lower level to the higher one, each routed level is projected into the higher one and run the maze algorithm another time to the higher level, which guarantees fewer congestions and less via count as it is a \textit{3D} routing algorithm, 
and the divide and conquer technique they use reduces the time taken. So the advantages of this paper are creating more efficient routing than \textit{2D} and \textit{3D} projection that used in most modern papers and reducing the runtime compared to the ordinary \textit{3D} maze routing. But there are some disadvantages too, one of them that the results are not efficient enough compared to the \textit{3D} routing algorithms, another one is that the runtime still high compared to \textit{2D} routers.

@@

    \bibitem{b14} Wu, Tai-Hsuan, Azadeh Davoodi, and Jeffrey T. Linderoth. "GRIP: scalable 3D global routing using integer programming." \textit{Proceedings of the 46th Annual Design Automation Conference}. 2009.

    \bibitem{b15} Xu, Yue, and Chris Chu. "MGR: Multi-level global router." \textit{2011 IEEE/ACM International Conference on Computer-Aided Design (ICCAD)}. IEEE, 2011.
